The Driving Forces of API Evolution

### 2015-05-25 thesis/paper.tex
Improved section in introduction - filling the gap

%Gap in Literature
Previous studies have investigated programming language APIs, libraries or frameworks focusing on causes and affects of modifications to APIs \cite{dig2005role, hou2011exploring, shi2011empirical}. However, to the best of our knowledge, no studies have been performed on embedded platform APIs from a software evolution perspective. Our study will fill this gap by analysing an embedded platform API by using software evolution theories and by classifying the types of changes that occur.

>>>>

%Gap in Literature
Previous studies have investigated programming language APIs, libraries or frameworks focusing on causes and affects of modifications to APIs \cite{dig2005role, hou2011exploring, shi2011empirical}. However, to the best of our knowledge, no studies have been performed on embedded platform APIs from a software evolution perspective. Our study will fill this gap by analysing an embedded platform API, classifying the types of changes that occur and analysing them with the use of software evolution theories.
